### 2017-03-29 CS798-ConvexityAndOptimization/assignments/assignment_02.tex
q2 template

>>>>

Let $A \in \R^{m\times n}$ and let $i$-th row of $A$ be denoted by $a_i$. Let $b \in \R^m$. We assume that each entry of $A$ and $b$ has absolute value at most $c$. To solve the system of linear inequalities we can reformulate as
$$\min_{x \in \R^n} f(x)$$
where $f(x) :=\max_{1\leq i \leq m} (b_i - a_ix)$. We attempt to approximate $f(x)$ with the $0$-convex soft-max function (for some parameter $K$):
$$g(x) := \frac{1}{K}\log \sum_{i=1}^m \exp (K(b_i - a_i x)).$$

%TODO compute the Hessian and determine for which \beta is g \beta-smooth

%TODO figure out which values of K and epilson' are needed so that we can find a point x with approximates f(x)-f(x^*) \leq \epsilon

%TODO propose algorithm: run gradient descent on g with K and \epsilon'

%TODO verify correctness and running time using theorem about gradient descent on \beta-smooth functions
